A geo-referenced micro-data set of real estate listings for the three largest Spanish cities from the Idealista website

### 2021-11-10 data-in-brief/dib-idealista18.tex
Anonymized the Data in Brief article
Submission to Computers, Environment and Urban Systems

\verso{D. Rey Blanco \textit{et al.}}

@@

%%Authors
\author[1]{David \snm{Rey Blanco}}
\author[1]{Pelayo \snm{González Arbués}}
% \author[1]{Pelayo \snm{González Arbues}\fnref{fn1}}
% \fntext[fn1]{This is author footnote for second author.}
\author[2]{Fernando \snm{López Hernández}}
\author[3]{Antonio \snm{Páez}\corref{cor1}}
%% Fourth author's email
\ead{paezha@mcmaster.ca}
\cortext[cor1]{Corresponding author:
  Tel.: +1-905-525-9140 ext 26099}

%%Affiliations
\address[1]{idealista, Plaza de las Cortes 5, 28014 Madrid, Spain}
\address[2]{Facultad de CC de la Empresa, Universidad Politécnica de Cartagena, C/ Real, 3. 30201 Cartagena, Murcia (Spain)}
\address[3]{School of Earth, Environment and Society, McMaster University, 1280 Main St W, Hamilton, Ontario L8S 4K1 Canada}

@@

\textbf{<article reference to be inserted>}

@@

%
%                          If you are describing secondary data, you are required to provide a list of
%                          the primary data sources used in the section.\newline
%
%                          Primary data sources:  ]\\
\hline
\hypertarget{target1}
{Data accessibility}   & Repository name: GitHub\newline
                         Direct URL to data: \url{https://github.com/paezha/idealista18}\newline
                         \\
\hline
Related
research\newline
article                & D. Rey Blanco, P. González Arbues, F. López Hernández, A. Páez, Using machine learning to identify spatial market segments: A reproducible study of major Spanish markets, Comput Environ Urban Syst. In Press.\newline
\end{longtable}
}
%%%

@@

The authors wish to thank Alessandro Galesi for his support in the paper revision and Juan Ramon Selva for collecting and cleaning the spatial data.

@@

David Rey Blanco and Pelayo González Arbués are emplyed by idealista. They have been granted permission to share the data presented in this articule. None of the authors have known competing financial interests or personal relationships which have, or could be perceived to have, influenced the work reported in this article.

>>>>

%\verso{D. Rey Blanco \textit{et al.}}
\verso{Author One \textit{et al.}}

@@

%%Authors
\author[1]{Author \snm{One}}
\author[2]{Author \snm{Two}}
%\author[1]{David \snm{Rey Blanco}}
%\author[2]{Pelayo \snm{Arbués González}}
% \author[1]{Pelayo \snm{González Arbues}\fnref{fn1}}
% \fntext[fn1]{This is author footnote for second author.}
%\author[3]{Fernando \snm{López Hernández}}
%\author[4]{Antonio \snm{Páez}\corref{cor1}}
%% Fourth author's email
%\ead{paezha@mcmaster.ca}
%\cortext[cor1]{Corresponding author:
%  Tel.: +1-905-525-9140 ext 26099}

%%Affiliations
%%\address[1]{idealista, Plaza de las Cortes 5, 28014 Madrid, Spain}
%%\address[2]{Facultad de CC de la Empresa, Universidad Politécnica de Cartagena, C/ Real, 3. 30201 Cartagena, Murcia (Spain)}
%%\address[3]{School of Earth, Environment and Society, McMaster University, 1280 Main St W, Hamilton, Ontario L8S 4K1 Canada}

@@

\textbf{article reference to be inserted}

@@

%
%                          If you are describing secondary data, you are required to provide a list of
%                          the primary data sources used in the section.\newline
%
%                          Primary data sources:  ]\\
\hline
\hypertarget{target1}
{Data accessibility}   & Repository name: GitHub\newline
                         Direct URL to data: \url{https://github.com/paezha/idealista18}\newline
                         \\
\hline
Related
research\newline
article                & Author One et al., Using machine learning to identify spatial market segments: A reproducible study of major Spanish markets, Comput Environ Urban Syst. In Press.\newline
\end{longtable}
}
%%%

@@

%The authors wish to thank Alessandro Galesi for his support in the paper revision and Juan Ramon Selva for collecting and cleaning the spatial data.
The authors wish to thank X for their support in the paper revision and Y for collecting and cleaning the spatial data.

@@

Author One and Author Two are employed by idealista. They have been granted permission to share the data presented in this article. None of the authors have known competing financial interests or personal relationships which have, or could be perceived to have, influenced the work reported in this article.
%David Rey Blanco and Pelayo González Arbués are employed by idealista. They have been granted permission to share the data presented in this articule. None of the authors have known competing financial interests or personal relationships which have, or could be perceived to have, influenced the work reported in this article.
